---
title: "DataProducts"
author: "RamyaChilakala"
date: "06/11/2020"
output: html_document
---
---
##Variation of mileage with respect to those features of the vehicle.
```{r}
library(plotly)
data(mtcars)
head(mtcars,100)
```
the data given by the google information we have made the  explortaory graphs useful for the human beings which they can be made to analyse relationship between the variables like mileage gives verse weigth of data like the cylinders count used in total, gears count the given cylinder has, carbs count the cylinds have in total. The relationship between horse power and mileage or qsec and mileage can also be checked. Our desired graph can be made as our custmers wanted it by taking the options and needs required for it are also to be considered.
In this the graph plated by me is between mileage(mpg) verses weight.
```{r}
plot_ly(mtcars) %>%
    add_trace(x = ~mpg, y = ~cyl, type="scatter", mode = "markers",name = "cyinder count", legendgroup = "cyinder count", 
              marker = list(color = "aliceblue")) %>%
    add_trace(x = ~mpg, y = ~gear, type="scatter", mode = "markers",
              name = "gears count", legendgroup = "gear count", 
              marker = list(color = "yellow3")) %>%
    add_trace(x = ~mpg, y = ~am, type="scatter", mode = "markers",
              name = "am count", legendgroup = "am count", 
              marker = list(color = "#AA4371")) %>%
    add_trace(x = ~mpg, y = ~vs, type="scatter", mode = "markers",
              name = "vs count", legendgroup = "vs count", 
              marker = list(color = "#c00000")) %>%
    add_trace(x = ~mpg, y = ~carb, type="scatter", mode = "markers",
              name = "carbs count in total", legendgroup = "carb count in total", 
              marker = list(color = "aquamarine1")) 
```
Scaterring plot is used above to acquire the required output.Different colors and its codes are used in my code above to distinguish the graph values easily and the understanding if the above graph is also easy because the colors mentioned are all different. The output of the above code gives us the count of the cylinders used, the count of the gears of the cylinders used,the count of the am of the cylinders,am count of the cylinders and the count of the carbs of the cylinders. From this assignment I have learnt how useful and easy scattering plot is and by using different colors distinguishing the categories is really easy.

